---
output:
  html_document: default
  pdf_document: default
---
# Include Libraries

```{r include=TRUE}
library(ggplot2)
library(readr)
library(plyr)
library(dplyr)
library(maps)
library(reshape2)
library(viridis)
```

```{r include=TRUE}
knitr::opts_chunk$set(fig.width=16, fig.height=8) 
```

# Read Data

```{r include=TRUE}
dataRate <- read.csv("Rate.csv", header = TRUE, stringsAsFactors = FALSE)
```

```{r include=TRUE}
head(dataRate)
```

# Chnage Age to integer

```{r include=TRUE}
dataRate$Age <- gsub('[a-zA-Z ]', '', dataRate$Age)
dataRate$Age <- gsub('-', '', dataRate$Age)
dataRate$Age <- as.integer(dataRate$Age)
```

# Explore Data

```{r include=TRUE}
head(dataRate)
```

```{r include=TRUE}
# Column Names
names(dataRate)
```

```{r include=TRUE}
summary(dataRate)
```

```{r include=TRUE}
# See data type of each column.
sapply(dataRate,class)
```

# Select subset of data

```{r include=TRUE}
planRateBenefit <- subset(dataRate, (dataRate$IndividualRate < "9999" & Age != "Family Option"),
                          select = c(StateCode, IssuerId, SourceName, Age, IndividualRate))
planRateBenefit <- na.omit(planRateBenefit)
sum(is.na(planRateBenefit))
```

```{r include=TRUE}
head(planRateBenefit)
```

# Groupby State Code And Do analysis of 

```{r include=TRUE}
stateGroupedData <- planRateBenefit %>% group_by(StateCode)
head(stateGroupedData)
```

## Group State By data with Source Name

```{r include=TRUE}
stateSourceGroupData <- stateGroupedData %>% group_by(SourceName) %>% summarise(IndividualRate = mean(IndividualRate))
head(stateSourceGroupData)
```

## Box Plot for State ID and IndividualRate

```{r include=TRUE}
ggplot(data = stateGroupedData, aes(x=StateCode, y=IndividualRate)) + geom_boxplot()
```

## Box Plot for State ID and Age

```{r include=TRUE}
ggplot(data = stateGroupedData, aes(x=StateCode, y=Age)) + geom_boxplot()
```

## Bar Graph for Source Count Per State

```{r include=TRUE}
StateSource <- stateGroupedData%>% count(SourceName)
head(StateSource)
```

```{r include=TRUE}
ggplot(StateSource, aes(fill=SourceName, y=n, x=StateCode)) + geom_bar(position="stack", stat="identity")
```

## Check Normality of Individual Rate

### Denisty Plot for IndividualRate

```{r include=TRUE}
ggplot(stateGroupedData, aes(x=IndividualRate))+geom_density(color="darkblue", fill="lightblue")+ geom_vline(aes(xintercept=mean(IndividualRate)),
            color="red", linetype="dashed", size=1)
```

### Q-Q Plot for IndividualRate

```{r include=TRUE}
ggplot(stateGroupedData, aes(sample=IndividualRate), preserveLabels=TRUE)+stat_qq()+stat_qq_line()+xlab("Standard Normal Quantiles for Individual Rate") + ylab("Quantiles for Individual Rate")
```

### Data Transformation

#### Log Transformation

```{r include=TRUE}
#
head(stateGroupedData)
stateGroupedData$IndividualRate <- log10(stateGroupedData$IndividualRate)
#is.na(stateGroupedData)
head(stateGroupedData)
```

### Density Plot after Log Transformation

### Density Plot for IndividualRate after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(x=IndividualRate))+geom_density(color="darkblue", fill="lightblue")+ geom_vline(aes(xintercept=mean(IndividualRate)),
            color="red", linetype="dashed", size=1)
```

### Q-Q Plot after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(sample=IndividualRate), preserveLabels=TRUE)+stat_qq()+stat_qq_line()+xlab("Standard Normal Quantiles for Individual Rate") + ylab("Quantiles for Individual Rate")
```

#### SquareRoot Transformation

```{r include=TRUE}
#
stateGroupedData <- planRateBenefit %>% group_by(StateCode)
head(stateGroupedData)
stateGroupedData$IndividualRate <- sqrt(stateGroupedData$IndividualRate)
#is.na(stateGroupedData)
head(stateGroupedData)
```

### Density Plot after SquareRoot Transformation

### Density Plot for IndividualRate after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(x=IndividualRate))+geom_density(color="darkblue", fill="lightblue")+ geom_vline(aes(xintercept=mean(IndividualRate)),
            color="red", linetype="dashed", size=1)
```

### Q-Q Plot after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(sample=IndividualRate), preserveLabels=TRUE)+stat_qq()+stat_qq_line()+xlab("Standard Normal Quantiles for Individual Rate") + ylab("Quantiles for Individual Rate")
```

#### CubeRoot Transformation

```{r include=TRUE}
#
stateGroupedData <- planRateBenefit %>% group_by(StateCode)
head(stateGroupedData)
stateGroupedData$IndividualRate <- stateGroupedData$IndividualRate^(1/3)
#is.na(stateGroupedData)
head(stateGroupedData)
```

### Density Plot after SquareRoot Transformation

### Density Plot for IndividualRate after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(x=IndividualRate))+geom_density(color="darkblue", fill="lightblue")+ geom_vline(aes(xintercept=mean(IndividualRate)),
            color="red", linetype="dashed", size=1)
```

### Q-Q Plot after Transformation

```{r include=TRUE}
ggplot(stateGroupedData, aes(sample=IndividualRate), preserveLabels=TRUE)+stat_qq()+stat_qq_line()+xlab("Standard Normal Quantiles for Individual Rate") + ylab("Quantiles for Individual Rate")
```

### Kruskal Walis Test

```{r include=TRUE}
kruskal.test(IndividualRate~StateCode, stateGroupedData)
```

# T Test 1 sample

```{r include=TRUE}
t.test(stateGroupedData$IndividualRate, mu = 500)
```

# Anova

```{r include=TRUE}
one_way <- aov(IndividualRate~StateCode, data = stateGroupedData)
summary(one_way)
```

## Check Dependance on Age

```{r include=TRUE}
one_way <- aov(IndividualRate~Age, data = stateGroupedData)
summary(one_way)
```

## Linear Regression


```{r include=TRUE}
lmIndividualRate = lm(IndividualRate ~ Age, data=stateGroupedData)
summary(lmIndividualRate)
```

# Correlation of Age and IndividualRate

```{r include=TRUE}
cor.test(~IndividualRate+Age, data=stateGroupedData)
```

# Scatterplot of Age and IndividualRate

```{r include=TRUE}
ggplot(stateGroupedData, aes(x=stateGroupedData$IndividualRate, y=stateGroupedData$Age)) + 
    geom_point()
```

```{r include=TRUE}
lmIndividualRate = lm(IndividualRate ~ Age+StateCode, data=stateGroupedData)
summary(lmIndividualRate)
```
